### 2015-03-10 Workshop2015/incremental.tex
Cleaning "energy" from the example
little changes

We consider a simplified SLA cloud contract inspired in the lowest contract provided by Azure: {\sf cost of \$0,05 cents per call,  8~GB of I/O volume/month, free data transfer cost within the same region,  01~GB of storage}. 
The user is ready to pay maximum {\sf \$1 as total query cost}; she requests that only {\sf certified} content providers are listed (provenance); at least {\sf 85$\%$} of precision of provided data, even if they are not fresh; she requires an availability rate of at least {\sf 90$\%$} in the next three hours and with a maximmum response time of {\sf 30} seconds for tutored contents and {\sf 0,5} seconds for online contents.

@@

Therefore, we propose a classification of SLA measures that represents the relationship between fine grained measures used by agreed SLAs and coarse grained measures used in user preferences statements. It specifies also how to compute coarse grained measures with fine grained ones. For example, data precision will be computed as a function of availability, freshness and provenance exported by data services. The derived SLA  can be seen as a set of unequations that have to be solved during the execution of a service composition. Since some of them can only be determined at execution time, the decision on which services will participate in the evaluation of the query is approximated. We will discuss this issue in the next sections.

@@

\begin{example}[Incremental queries]\label{Ex:rew2}
Let us return to the energy trade system of Example~\ref{Ex:rew1}.
 Suppose that the user requires to retrieve a list of star providers  daily and weekly that can deliver ``\textit{5 Go}'' of expert content about Emily Dickinson peotry.
In this case, each individual and hub database will be queried and the list will be produced by adding data obtained from them, until the 5Go  capacity is reached.
Let us suppose that, in order to minimize the the communications between servers, the lists need to be produced incrementally.
In this case, the composition produced by the service refinement may need to include an iteration (to aggregate partial results). 
The data produced by the warehouse servers will be processed in batch and the process will end once the list reaches the desired capacity.

@@

Second, precalculated queries and partial results can be also stored in cache or in a persistent support. Rewriting results can be also stored and reduce execution and resources consumption time when evaluating similar queries. Storing or not such SLAs will depend on the cloud subscription of the user the issued the query (data access, intermediate storage capacity , cost of storage , etc ... ).

>>>>

We consider a simplified SLA cloud contract inspired in the lowest contract provided by Azure: {\sf cost of \$0,05 cents per call,  8~GB of I/O volume/month, free data transfer cost within the same region,  01~GB of storage}. 
The user is ready to pay maximum {\sf \$1 as total query cost}; she requests that only {\sf certified} content providers are listed (provenance); at least {\sf 85$\%$} of precision of provided data, even if they are not fresh; she requires an availability rate of at least {\sf 90$\%$} in the next three hours and with a maximum response time of {\sf 30} seconds for tutored contents and {\sf 0,5} seconds for online contents.

@@

Therefore, we propose a classification of SLA measures that represents the relationship between fine grained measures used by agreed SLAs and coarse grained measures used in user preferences statements. It specifies also how to compute coarse grained measures with fine grained ones. For example, data precision will be computed as a function of availability, freshness and provenance exported by data services. The derived SLA  can be seen as a set of inequations that have to be solved during the execution of a service composition. Since some of them can only be determined at execution time, the decision on which services will participate in the evaluation of the query is approximated. We will discuss this issue in the next sections.

@@

\begin{example}[Incremental queries]\label{Ex:rew2}
Let us return to the content  trade system of the MOOC Example~\ref{Ex:rew1}.
 Suppose that the user requires to retrieve a list of star providers  daily and weekly that can deliver ``\textit{5 Go}'' of expert content about Emily Dickinson poetry.
In this case, each individual and hub database will be queried and the list will be produced by adding data obtained from them, until the 5Go  capacity is reached.
Let us suppose that, in order to minimize the the communications between servers, the lists need to be produced incrementally.
In this case, the composition produced by the service refinement may need to include an iteration (to aggregate partial results). 
The data produced by the warehouse servers will be processed in batch and the process will end once the list reaches the desired capacity.

@@

Second, pre-computed queries and partial results can be also stored in cache or in a persistent support. Rewriting results can be also stored and reduce execution and resources consumption time when evaluating similar queries. Storing or not such SLAs will depend on the cloud subscription of the user the issued the query (data access, intermediate storage capacity , cost of storage , etc ... ).
